Timeliness of security updates for Android

### 2014-08-07 securityupdates.tex
Add draft update ecosystem figure
Note the start and end date of DA and AVO data
Add numbers or placeholders to update ecosystem diagram

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{tikz}
\RequirePackage[date=terse,isbn=true,doi=true,url=false,urldate=iso8601,maxbibnames=9,backref=false,backend=bibtex]{biblatex}
\addbibresource{securityupdates.bib}
\renewcommand{\bibfont}{\small}

@@

\input{dastats}
\input{avostats}
\newcommand{\percMarketShare}{XX\%~\cite{TODO}}
\newcommand{\daNumNetworkOperators}{XXX~[\S\ref{sec:results}]}
\newcommand{\daNumDevices}{XXXX}
\newcommand{\daDeviceDays}{XXXXX}
\newcommand{\daMonths}{X}% Number of months for which we have the below number of devices
\newcommand{\daMonthsDevices}{XXX}

@@

\subsection{Android update process}
TODO

\section{Results}
\label{sec:results}
In this section we present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root vulnerabilities on average, nexus devices to be better than others, \daSecScoreBestmanufacturer\ to be the best manufacturer and ????. %TODO summarise our results
%TODO comparison of nexus update rates with iOS

>>>>

\documentclass[conference,a4paper,twoside]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\graphicspath{figures/}
\usepackage{import}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{tikz}
\RequirePackage[date=terse,isbn=true,doi=true,url=false,urldate=iso8601,maxbibnames=9,backref=false,backend=bibtex]{biblatex}
\addbibresource{securityupdates.bib}
\renewcommand{\bibfont}{\small}

@@

\input{dastats}
\input{avostats}
\newcommand{\percMarketShare}{XX\%~\cite{TODO}}
\newcommand{\daNumNetworkOperators}{XXX~[\S\ref{sec:results}]}
\newcommand{\daNumDevices}{XXXX}
\newcommand{\daDeviceDays}{XXXXX}
\newcommand{\daMonths}{X}% Number of months for which we have the below number of devices
\newcommand{\daMonthsDevices}{XXX}
% Num versions since \daStartDate
\newcommand{\bouncyCastleNumVersions}{A}
\newcommand{\opensslNumVersions}{B}
\newcommand{\apacheLibsNumVersions}{C}
\newcommand{\apacheLibsNumLibs}{E}
\newcommand{\linuxNumVersions}{D}

@@

\subsection{Android update process}
\begin{figure}
 \centering
 \def\svgwidth{\columnwidth}
 \import{figures/}{update_ecosystem.pdf_tex}
 \caption{Flow of updates between participants in the Android ecosystem.
 Numbers on edges indicate updates shipped between \daStartDate\ and \daEndDate, numbers in brackets represent number of such entities in our data.}
 \label{fig:update_ecosystem}
\end{figure}
\cite{Vidas2011}
TODO

\section{Results}
\label{sec:results}
In this section we present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root vulnerabilities on average, nexus devices to be better than others, \daSecScoreBestmanufacturer\ to be the best manufacturer and ????. %TODO summarise our results
The Device Analyzer data used here was collected between \daStartDate\ and \daEndDate.
The \texttt{androidvulnerabilities.org} data was collected between \avoStartDate\ and \avoEndDate.
%TODO comparison of nexus update rates with iOS
